---
title: "vignette"
output: pdf_document
date: "2023-11-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This vignette is intended to demonstrate the usage of this package, which is to
plot the ...

## Setting Up
Since this package is under heavy construction, make sure to download
and import the R development tool `devtools` with the following command in order
to run all the commands

```{r}
# install.packages("devtools")
library("devtools")
library("RcolorBrewer")
load_all()
```

Then run the following command to create the `data` and `output` folders. You only
need to run this once

```{r}
if (!dir.exists("data/")){
  dir.create("data/")
}

if (!dir.exists("output/")){
  dir.create("output/")
}
```


## Loading Data

Once the above procedures are completed, move the excel file into the `data` folder.
Open up the excel file, and fill in the two variables `ion_table_loc` and 
`iso_table_loc` with the top left and bottom right cell of each table. Make sure
that the column and row names are also included here.


```{r}
file_loc <- "data/Datacorrected_20231110-ET.xlsx"

ion_table_loc <- "A43:AB81"
iso_table_loc <- "A84:AC305"

ion_count <- readxl::read_xlsx(file_loc,
                               range = ion_table_loc)

iso_abun <- readxl::read_xlsx(file_loc,
                              range = iso_table_loc)
```


###
